---
title: "Psychological Research Preregistration-Quantitative (aka PRP-QUANT) Template"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Psychological Research Preregistration-Quantitative (aka PRP-QUANT) Template}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette shows the Psychological Research Preregistration-Quantitative (aka PRP-QUANT) Template form. It can be initialized as follows:

```{r, eval=FALSE}
initialized_prpQuant_v1 <-
  preregr::prereg_initialize(
    "prpQuant_v1"
  );
```

After this, content can be specified with [preregr::prereg_specify()](https://r-packages.gitlab.io/preregr/reference/prereg_specify.html) or [preregr::prereg_justify](https://r-packages.gitlab.io/preregr/reference/prereg_justify.html). To check the next field(s) for which content still has to be specified, use [preregr::prereg_next_item()](https://r-packages.gitlab.io/preregr/reference/prereg_next_item.html).

The form is defined as follows (use [preregr::form_show()](https://r-packages.gitlab.io/preregr/reference/form_show.html) to show the form in the console, instead):

```{r}
preregr::form_knit(
  "prpQuant_v1"
);
```
